
title: "W_UP_01"
author: "Cienna Baker-Salgado"
date: "9 September 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players 

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Positions are the categorical variables. Push-ups are the numerical variables. I will do an analysis that explains push-ups based on position
# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(pushups~position,data=mydata)
```
<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-

The push-ups are on the y-axis and positions on the x-axis of the box plot. On the box plot, there is a large segment on each whisker plot. The average push-ups for the positions looks to be different. The skill position seems to do more push-ups based off of the y-axis (pushups)

### Numerical Descriptive Results
```{r}
favstats(pushups~position,data=mydata)
```


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


The median for the two positions has a major difference. The median for the skill position is higher than the line positions. The line positions at maximum can do  34 push ups and the skill can do up to 108. From the data results it seems that skill positions are far more capable to do the most push ups.

## Inferential Results
```{r}
t.test(pushups~position,data=mydata)
```


<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


The p-value is 0.000009421, the df value is 27.079, and the t-value is -5.4341. Our alternative hypothesis is shown and states true differences in means between group LINE and group SKILL is not equal to 0. Mean in group LINE is 17.12500; Mean in group SKILL is 49.72. If our null hypothesis is true, the p value is the probability of getting our results. LINE vs SKILL. The p-value is so small that it would ignore the null hypothesis and if it were to be greater than .05, you did not reject the null hypothesis. If you reject the null hypothesis, it's possible that the SKILL group can do more push-ups.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was "Who could do the most push-ups?" The SKILL position or the LINE position under a specific amount of time?" Based off of our numerical descriptive results & our inferential results, we can see that the SKILL position can do more push-ups than the LINE position under any amount of time. We used a box plot and a table to figure out our values and percentages. The median and average were much higher for the SKILL position.
